---
title: "R Notebook"
output: html_notebook
---

```{r}
shuff_data <- read.table(file="shuff_score.txt")
```

```{r}
shuff_mean = mean(shuff_data[,1])
shuff_sd = sd(shuff_data[,1])
z_score_915 = (915 - shuff_mean)/shuff_sd
pnorm_915 = pnorm(915, mean = shuff_mean, sd = shuff_sd, lower.tail = FALSE)
```

  Yes, a Z-score of ~140.5 is highly significant in a normal distribution.
  1.96 is the typical 5% upper cutoff for a normal distribution, consisting of the upper 2.5%.
  This is not particularly useful since this is not a normal distribution but a right skewed one. Sill, our z-score is so significantly far right that it seems to indicate a lack of randomness.
    Yes, I believe we should correct this for another hypothesis. Specifically, we should do a one tailed test, for which we can vary our P-value to see our level of confidence.
      When using a right tail test, our P value here is basically 0, and appears as 0 in the code due to rounding. This means that at a 0.000001 or so significance level (very high confidence) we reject the null hypothesis, and it suggests that this value is not random.
      For instance, if we wanted to be 95% certian that our results were random, we would expect a p-value that is less than or equal to .05. The p-value we see here blows this out of the water, as it is essencially 0.
      I would likely use a 99.99% certainty threshold (0.0001) for biological alignment, simply because the resources that go into research are best spent in situations where we are very certian.
      
```{r}
NP_414543.1.align <- read.table(file="NP_414543.1_align.txt")
```    

```{r}
boxplot(NP_414543.1.align[,1], horizontal=TRUE)
boxplot(shuff_data[,1], horizontal=TRUE)
```

```{r}
x1= subset(NP_414543.1.align, NP_414543.1.align[,1] < 250)
x2= x1[,1]
hist(x2, breaks=seq(range(x2)[1]-1, range(x2)[2]+1, by=0.5))
```

```{r}
x=shuff_data[,1]
hist(x, breaks=seq(range(x)[1]-1, range(x)[2]+1, by=0.5))
```

```{r}
mycolors = rainbow(2)
ggplot(NP_414543.1.align, aes(V1)) +
  geom_density()
ggplot(x1, aes(V1)) +
  geom_density()
ggplot(shuff_data, aes(V1)) +
  geom_density()
```

```{r}
NP_414543.1.align = NP_414543.1.align %>% 
  mutate(new_col = "exp")
shuff_data = shuff_data %>% 
  mutate(new_col = "shuff")
my_full_data = rbind(shuff_data, NP_414543.1.align, by="V1")
my_full_data = my_full_data %>% 
  filter(V1 != "V1") %>% 
  mutate(V1 = as.numeric(V1))
```

```{r}
boxplot(my_full_data$V1, horizontal=TRUE)
```

```{r}
p2 <- ggplot(data=my_full_data, aes(x=log10(my_full_data$V1), group=new_col, fill=new_col)) +
    geom_boxplot(adjust=1.5, alpha=.4)
p2
p1 <- ggplot(data=my_full_data, aes(x=log10(my_full_data$V1), group=new_col, fill=new_col)) +
    geom_density(adjust=1.5, alpha=.4)
p1
```

```{r}

```

